### 2013-09-24 evaluation/paper.tex
freakingtable !!!!
finish off table

\subsection{Superpixel CRFs for Semantic Segmentation}
Our main attention is devoted to the use of conditional random fields for
semantic segmentation.  We use the Pascal VOC and MSRC datasets. A detailed
description of the method will be given in Chapter~\ref{ch:exact_learning}.
%TODO will it?
The Pascal VOC has \ldots training and \ldots validation images, each having
around 100 superpixels. There are 20 object categories, plus background. The % TODO check! refer to other part
MSRC dataset has \ldots training and \ldots test images, also segmented in
around 100 superpixels each. We use the MSRC-21 dataset, which has 21 target
classes.
Each superpixel is represented as an output variable, with the ground truth obtained
by majority vote over the pixel belonging to the superpixel. We removed all
superpixels which were mostly ``void'', leading to some samples haven much
fewer than 100 variables.
Pairwise potentials were introduced for each pair of neighboring superpixels.
We then removed all superpixels that were labeled as ``void'', together with
their pairwise potentials.
As unary potentials, we use the TextonBoost probabilities provided by  % FIXME this !!
\citet{krahenbuhl2012efficient}.  We average probabilities inside each
superpixel, yielding 21 input features for both datasets.  We also used the
same pairwise features for the two datasets: a constant feature, a color
contrast feature, and a feature encoding relative vertical position between
superpixels.  Overall, the models for both datasets had $21 \cdot 21 + 21^2
\cdot 4$ features.  It is possible to assume symmetric potentials for this
dataset, leading to less pairwise features. We found both parametrizations
yielded similar results.

\begin{table}
    \caption{Summary of Datasets.\tablabel{datasets}}
    \begin{tabu} to \linewidth{@{}XXXXXX@{}}
    %\multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\
    \toprule
    Dataset    & samples & nodes & edges & dim w & labels\\
    \cmidrule{1-6}
    MNIST      & 60000   & 1     & none  & 7840  & 10\\
    OCR-small  & 704     & 3--14 & chain & 1444  & 26\\
    OCR-large  & 6173    & 3--14 & chain & 1444  & 26\\
    scene-tree & 1211    & 6     & tree  & 1244  & 2\\
    scene-full & 1211    & 6     & loopy & 1284  & 2\\
    yeast-tree & 1500    & 14    & tree  & 1494  & 2\\
    yeast-full & 1500    & 14    & loopy & 1806  & 2\\
    snake      & 200     &84--168& loopy & 22275 & 11\\
    MSRC21     & 276     & 7--113& loopy &       & 21\\
    Pascal VOC & 964     & 8--112& loopy &       & 21\\
    \bottomrule

>>>>

\subsection{Superpixel CRFs for Semantic Segmentation}
Our main attention is devoted to the use of conditional random fields for
semantic segmentation.  We use the Pascal VOC and MSRC datasets. A detailed
description of the method will be given in Chapter~\ref{ch:exact_learning}.
%TODO will it?
The Pascal VOC has \ldots training and \ldots validation images, each having
around 100 superpixels. There are 20 object categories, plus background. The % TODO check! refer to other part
MSRC dataset has \ldots training and \ldots test images, also segmented in
around 100 superpixels each. We use the MSRC-21 dataset, which has 21 target
classes.
Each superpixel is represented as an output variable, with the ground truth obtained
by majority vote over the pixel belonging to the superpixel. We removed all
superpixels which were mostly ``void'', leading to some samples haven much
fewer than 100 variables.
Pairwise potentials were introduced for each pair of neighboring superpixels.
We then removed all superpixels that were labeled as ``void'', together with
their pairwise potentials.
We use the unary and pairwise potentials described in \Secref{semantic_segmentation}:
for the Pascal VOC dataset 21 unary potentials and 63 for the MSRC21 dataset.
We use the same three pairwise features for both dataset: a constant, a color
feature and a feature encoding relative vertical position.
Overall, this results in $21 \cdot  21 + 3 \cdot 21 \cdot 21 = 1764$ parameters
for the potentials on Pascal VOC and $63 \cdot  21 + 3 \cdot 21 \cdot 21 =
2646$ parameters for the potentials on the MSRC21 dataset.

%For Pascal VOC we use the probabilities provided by
%\citet{krahenbuhl2012efficient}, which combine low-level Texton-Boost
%potentials with bounding-box object detectors.  We average probabilities inside
%each superpixel, yielding 21 input features for both datasets.  We also used
%the
%same pairwise features for the two datasets: a constant feature, a color
%contrast feature, and a feature encoding relative vertical position between
%superpixels.  Overall, the models for both datasets had $21 \cdot 21 + 21^2
%\cdot 4$ features.  It is possible to assume symmetric potentials for this
%dataset, leading to less pairwise features. We found both parametrizations
%yielded similar results.

\begin{table}
    \caption{Summary of Datasets.\tablabel{datasets}}
    \begin{tabu} to \linewidth{@{}X[1,l]YX[1,c]X[1,c]YY@{}}
    %\multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\
    \toprule
    Dataset    & {samples} & nodes & edges & {dim w} & {labels}\\
    \cmidrule{1-6}
    MNIST      & 60000   & 1     & none  & 7840  & 10\\
    OCR-small  & 704     & 3--14 & chain & 1444  & 26\\
    OCR-large  & 6173    & 3--14 & chain & 1444  & 26\\
    scene-tree & 1211    & 6     & tree  & 1244  & 2\\
    scene-full & 1211    & 6     & loopy & 1284  & 2\\
    yeast-tree & 1500    & 14    & tree  & 1494  & 2\\
    yeast-full & 1500    & 14    & loopy & 1806  & 2\\
    snake      & 200     &84--168& loopy & 22275 & 11\\
    MSRC21     & 276     & 7--113& loopy &  1764 & 21\\
    Pascal VOC & 964     & 8--112& loopy &  2646 & 21\\
    \bottomrule
